NEW TITLE

### 2019-11-01 paper.tex

@@

Humans are able to determine the 3D position of a sound source and by exploiting this natural ability, the real-time guidance instructions can be interpreted without posing a significant cognitive load.
A sound source can be spatialised by adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance).
In our case, only the pan and elevation positions are transmitted to the user to point the camera towards a target object or visual feature.
However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
In~\cite{lock2019bone}, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals sued with expensive closed-cup headphones~\cite{macdonald2006spatial}.
We expand upon the initial investigation in~\cite{lock2019bone} with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error. 
The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.

@@

Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
The majority of these systems rely on one or a combination of vocal~\cite{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\cite{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\cite{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
In general, participants with visual impairments report that they prefer haptic and vocal feedback out of the three options~\cite{arditi2013user}.
However, haptic feedback systems typically have extra hardware requirements to transmit the guidance instructions.
Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\cite{arditi2013user}.
Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.

Simple audio tones and vocal feedback signals have been used in conjunction with cameras and object detectors to communicate their relative positions to the user with a reasonable level of accuracy~\cite{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\cite{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}. 
This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\cite{stanley2006lateralization}.
In~\cite{durette2008visuo}, they transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\cite{lock2019bone}.
We expand upon this preliminary study with a more thorough investigation into the participants' performance and how changes to the audio signal's behaviour can impact that performance.

Researchers have previously used Fitts's Law~\cite{fitts1954information}, and more recently MacKenzie's modified version of it~\cite{mackenzie1992fitts}, as a metric to evaluate the performance of a spatial audio HMI\@.
Fitts's Law was originally proposed for visual target search tasks, but has since been applied in non-visual target search tasks as well.
For example, experiments with a haptic feedback pointing device have been performed to evaluate how effective it was at directing a user towards a target~\cite{ahmaniemi2009augmented} and the authors showed that the search time adheres to Fitts's Law.
However, they also note that it is not a perfect fit, citing the fact that Fitts's Law does not take into account a user's search strategy.
Another group of researchers conducted experiments using a spatial audio interface to describe the position of a target on the horizontal plane~\cite{marentakis2006effects}.
Here, participants pointed to where they thought the targets were, on their left or right, as they traversed a path.
Their results show a good relation between target difficulty and search time, providing a strong argument that Fitts's Law can be used to describe the performance of a spatial audio interface.
These results have since been supported by other authors, who found that Fitts's Law provided a good explanation for the results from an experiment using visual, limited visual and non-visual feedback cues~\cite{wu2010fitts}.
However, Fitts's Law has not yet been shown to apply to a spatial tone that uses varying pitch to convey the target's tilt angle, as demonstrated in this paper.

@@

A set of bone-conduction headphones is used as the audio transmission medium.
These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still relies on sound to detect, for example, oncoming vehicles and people~\cite{lichtenstein2012headphone}.
Alternative solutions that allow ambient noise through, such as open-back headphones, were also considered, but they still filter the incoming sound and were therefore disregarded.
The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected since they do not interfere on other sounds and are also more discreet than the larger over-ear headphones.

@@

When an audio signal is transmitted via a set of speakers or headphones, it can be transformed with an HRTF to mimic the characteristics of a natural sound source before it is transmitted, making the brain believe a sound is located at some arbitrary position.
An HRTF is a mathematical function that simulates the response signal of a human head and is derived by capturing key characteristics that affect the monaural and binaural responses, such as the user's hearing levels and head size.
Since hearing responses are unique amongst different users, the best results would be observed if each user had their own customised HRTF.\
However, given the complicated process involved to capture the required user characteristics, making unique HRTFs is often an untenable solution and using average values (e.g.\ head measurements, height, etc.) have shown to produce acceptable results~\cite{gardner1995hrtf}.

The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \cref{fig:cam-coords}.
Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\cite{klatzky2006cognitive}.
However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.

>>>>

\articletype{Review Draft}

\title{NEW TITLE}

\author{%
  \name{Jacobus C. Lock\textsuperscript{a}\thanks{Contact Author}, Iain D. Gilchirst\textsuperscript{b}, Grzegorz Cielniak\textsuperscript{a} and Nicola Bellotto\textsuperscript{a}}%
  \affil{\textsuperscript{a}University of Lincoln, Lincoln, LN6 7TS, UK; \textsuperscript{b}University of Bristol, Bristol, BS8 1TH, UK}%
}

\maketitle

\begin{abstract}
  The ActiVis project's aim is to build a mobile guidance aid to help people with limited vision find objects in an unknown environment.
  This system uses bone-conduction headphones to transmit audio signals to the user and requires an effective non-visual interface.
  In prior work, we implemented and tested a audio-based interface that uses a spatialised signal to convey a target's position on the horizontal plane. 
  This approach was shown to work well and in this work we expand the number of tests and metrics to provide a more more in-depth evaluation of the proposed audio interface.
  Specifically, we used a larger number of participants and found design limitations and a Fitts's Law-compliant trend that we can use to improve and refine the audio signals. 
\end{abstract}

\begin{keywords}
  Visual impairment; active vision; guidance system; audio interface; Fitts Law
\end{keywords}

@@

Humans are able to determine the 3D position of a sound source and by exploiting this natural ability, the real-time guidance instructions can be interpreted without posing a significant cognitive load.
A sound source can be spatialised by adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance).
In our case, only the pan and elevation positions are transmitted to the user to point the camera towards a target object or visual feature.
However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals sued with expensive closed-cup headphones~\citep{lock2019bone,macdonald2006spatial} and we expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error. 
The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.

@@

Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
The majority of these systems rely on one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
In general, participants with visual impairments report that they prefer haptic and vocal feedback out of the three options~\citep{arditi2013user}.
However, haptic feedback systems typically have extra hardware requirements to transmit the guidance instructions.
Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.

Simple audio tones and vocal feedback signals have been used in conjunction with cameras and object detectors to communicate their relative positions to the user with a reasonable level of accuracy~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}. 
This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\cite{stanley2006lateralization}.
In~\cite{durette2008visuo}, they transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\cite{lock2019bone}.
We expand upon this preliminary study with a more thorough investigation into the participants' performance and how changes to the audio signal's behaviour can impact that performance.

Researchers have previously used Fitts's Law~\citep{fitts1954information}, and more recently MacKenzie's modified version of it~\citep{mackenzie1992fitts}, as a metric to evaluate the performance of a spatial audio HMI\@.
Fitts's Law was originally proposed for visual target search tasks, but has since been applied in non-visual target search tasks as well.
For example, experiments with a haptic feedback pointing device have been performed to evaluate how effective it was at directing a user towards a target~\citep{ahmaniemi2009augmented} and the authors showed that the search time adheres to Fitts's Law.
However, they also note that it is not a perfect fit, citing the fact that Fitts's Law does not take into account a user's search strategy.
Another group of researchers conducted experiments using a spatial audio interface to describe the position of a target on the horizontal plane~\citep{marentakis2006effects}.
Here, participants pointed to where they thought the targets were, on their left or right, as they traversed a path.
Their results show a good relation between target difficulty and search time, providing a strong argument that Fitts's Law can be used to describe the performance of a spatial audio interface.
These results have since been supported by other authors, who found that Fitts's Law provided a good explanation for the results from an experiment using visual, limited visual and non-visual feedback cues~\citep{wu2010fitts}.
However, Fitts's Law has not yet been shown to apply to a spatial tone that uses varying pitch to convey the target's tilt angle, as demonstrated in this paper.

@@

A set of bone-conduction headphones is used as the audio transmission medium.
These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
=======
This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still relies on sound to detect, for example, oncoming vehicles and people~\cite{lichtenstein2012headphone}.
Alternative solutions that allow ambient noise through, such as open-back headphones, were also considered, but they still filter the incoming sound and were therefore disregarded.
The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected since they do not interfere on other sounds and are also more discreet than the larger over-ear headphones.

@@

When an audio signal is transmitted via a set of speakers or headphones, it can be transformed with an HRTF to mimic the characteristics of a natural sound source before it is transmitted, making the brain believe a sound is located at some arbitrary position.
An HRTF is a mathematical function that simulates the response signal of a human head and is derived by capturing key characteristics that affect the monaural and binaural responses, such as the user's hearing levels and head size.
Since hearing responses are unique amongst different users, the best results would be observed if each user had their own customised HRTF.\
However, given the complicated process involved to capture the required user characteristics, making unique HRTFs is often an untenable solution and using average values (e.g.\ head measurements, height, etc.) have shown to produce acceptable results~\citep{gardner1995hrtf}.

The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \cref{fig:cam-coords}.
Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\citep{klatzky2006cognitive}.
However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
